CommonMind Consortium: DLPFC

### 2021-01-14 combined_analysis/combine_all_DLPFC.Rmd
For public release

show_zenith_results( res_meta_zenith, "DxSCZ", "GO", FDR=0.05)
show_zenith_results( res_meta_zenith, "DxSCZ", "MSigDB", FDR=0.05)
```

@@

 plot_zenith_results( res_meta_zenith, "DxSCZ", "GO", FDR=0.05) 
```

```{r, fig.width=9}
  plot_zenith_results( res_meta_zenith, "DxSCZ", "MSigDB", FDR=0.05)  
```

>>>>

show_zenith_results( res_meta_zenith, "DxSCZ", "GO", FDR=0.5)
show_zenith_results( res_meta_zenith, "DxSCZ", "MSigDB", FDR=0.5)
```

@@

 plot_zenith_results( res_meta_zenith, "DxSCZ", "GO", FDR=0.5) 
```

```{r, fig.width=9}
  plot_zenith_results( res_meta_zenith, "DxSCZ", "MSigDB", FDR=0.5)  
```
